Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-11-13 documents/Archive/main.tex
More progress, slides to present found inequalities

    \section{The Fritz Distribution}
    \label{sec:fritz_dist}
    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario~\cite{Fritz_2012}. Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
    \begin{align*}
    \eq \label{eq:fritz_dist}
    \begin{split}
    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
    \end{split}
    \end{align*}
    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
    \begin{equation}
    \begin{gathered}
    \label{eq:fritz_quantum_realization}
    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gathered}
    \end{equation}
    Where for convenience of notation $\psi_x$ is used to denote the superposition,
    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.

    Fritz first proved it's incompatibility~\cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario. In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality. To illustrate this, begin with the CHSH inequality~\cite{CHSH_Original},
    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively. Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
    \begin{gather*}
    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
    \end{gather*}
    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$~\cite{Cirelson_1980}.

>>>>

    \section{The Fritz Distribution}
    \label{sec:fritz_dist}
    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario~\cite{Fritz_2012}. Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
    \begin{align*}
    \eq \label{eq:fritz_dist}
    \begin{split}
    \prob[F][000] = \prob[F][110] = \prob[F][301] = \prob[F][211] = \prob[F][122] = \prob[F][032] = \prob[F][233] = \prob[F][323] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][010] = \prob[F][100] = \prob[F][311] = \prob[F][201] = \prob[F][132] = \prob[F][022] = \prob[F][223] = \prob[F][333] &= \f{1}{32}\br{2 - \sqrt{2}}
    \end{split}
    \end{align*}
    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
    \begin{equation}
    \begin{gathered}
    \label{eq:fritz_quantum_realization}
    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gathered}
    \end{equation}
    Where for convenience of notation $\psi_x$ is used to denote the superposition,
    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.

    Fritz first proved it's incompatibility~\cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario. In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality. To illustrate this, begin with the CHSH inequality~\cite{CHSH_Original},
    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively. Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
    \[ \ba{AB|C=1} + \ba{AB|C=2} + \ba{AB|C=3} - \ba{AB|C=0} \leq 2 \eq \label{eq:chsh_c}\]
    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
    \[ \ba{AB} \defined 2\bc{\prob[][00] + \prob[][03] + \prob[][30] + \prob[][33] + \prob[][11] + \prob[][12] + \prob[][21] + \prob[][22]} - 1 \]
    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
    \begin{gather*}
    \ba{AB|C=1} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
    \ba{AB|C=2} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
    \end{gather*}
    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$~\cite{Cirelson_1980}.
